Article title

### 2017-07-31 paper-webserver.tex
CHANGE: first para is weird, slight restructuring

% costs of bacterial infections
Foodborne ilnesses are increasingly difficult to track; food is globally sourced and consumers are purchasing more prepared ingrediants \cite{kozak2013foodborne}.
The resulting consumer infections translate into actual costs: in Canada alone, an estimated 4000 hospitalizations and 105 deaths per year are thought to be the result of various pathogens \cite{thomas2015estimates}.
Futhermore, the associated economic costs have been known for decades \cite{todd1989costs}.
% surveillance
Public-health agencies routinely monitor emerging threats, of which \textit{Salmonella enterica} and \textit{Escherichia coli} are amongst the two most common \cite{kozak2013foodborne}.
In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, a variety of bioinformatic approaches are now based on whole-genome sequencing (WGS).

>>>>

% costs of bacterial infections
Foodborne ilnesses are increasingly difficult to track; ingrediants are sourced globally and contamination can occur at any point in the supply-chain.
The resulting consumer infections translate into actual costs: in Canada, an estimated 4000 hospitalizations and 105 deaths per year are thought to be the result of various pathogens \cite{thomas2015estimates}.
In the United States, this figure is 55961 hospitalizations and 1351 deaths per year \cite{scallan2011foodborne}.
Futhermore, the associated economic costs have been known for decades \cite{todd1989costs}.
% surveillance
Public-health agencies routinely monitor emerging threats, of which \textit{Salmonella enterica} and \textit{Escherichia coli} are amongst the two most common \cite{kozak2013foodborne}.
In \textit{Salmonella enterica} \cite{bell2016recent}, \textit{Escherichia coli} \cite{fratamico2016advances}, and others pathogens \cite{ronholm2016navigating}, a variety of bioinformatic approaches are now based on whole-genome sequencing (WGS).
